\subsubsection{Achieved objectives}

%Were the project objectives achieved? \label{q} \newline

%TOD based on the low amount of requirements, this doesn't say much.
The project requirements written in Table~\ref{tab:requirements-with-scope} turned out to be well-thought as majority was implemented. By successfully establishing single-machine non-containerized simulation of apnea predictions minimal viable product was delivered. This was further more extended --- using Docker --- to multi-machine containerized setup. On top, additional security was configured with TLS certificate requirement between the all communicating nodes. Although this security might not be necessary since it was done in a single network, the federated setup is ready to be tested in a multi-network environment where this would become a must. All requirements with associated completion status can be seen in Table~\ref{tab:requirements-with-scope-and-completion}.

\begin{table}[htb]\centering
    \caption{Functional requirements with their importance and completion status, higher rows correspond to higher priority. For a further dissection of minimal viable requirements, see Appendix~\ref{appendix:backlog}}\label{tab:requirements-with-scope-and-completion}
    \csvreader[
        tabular = | p{0.15\textwidth} | p{0.6\textwidth} | p{0.15\textwidth} |,
        table head = \hline \textbf{Importance} & \textbf{Requirement} & \textbf{Implemented}\\\hline,
        late after line = \\\hline,
        separator = semicolon
    ]{media/requirements-with-scope-and-completion.csv}%
    {Importance=\importance, Requirement=\requirement, Implemented=\implemented}{%
        \importance & \requirement & \implemented
    }
\end{table}

However, there are still some unresolved issues. One of them being the aggregated evaluation metrics showing presumably wrong results when it comes to precision and recall scores --- these are always zero, in contrast to centralized training where this does not happen. On the other hand, the train metrics are correct, which is why the task is deemed achieved, besides that my focus was not on improving model performance. Perhaps testing the final model on all data would be an indicator about the direction of the issue --- were the metrics not aggregated correctly, or is there an issue solely in the evaluation code.

A summary of final metrics from both centralized and federated approaches can be seen in Table~\ref{tab:second-test}. The differance between these two machine learning techniques, in terms of metrics, turn out to be very minor, around 0.03 $\pm$ 0.05, with federated learning mostly having slightly lower values; except for the test metrics, where we suspect a minor bug in the code. Results of another test can be found in Appendix~\ref{appendix:second-test}, all tests and project code can also be found on GitHub\footnote{https://github.com/OP4LIFE/federated-learning-approach-for-obstructive-sleep-apnea-prediction}.

\begin{table}[htb]\centering
    \caption{Results of centralized and federated learning approach and their comparison. In a federated setting, the test consisted of 3 hospitals (clients), 5 rounds and 15 epochs. In a centralized setting, it consisted of $15\cdot5\cdot3$ epochs (255 epochs). Hyperparameters were the same for both approaches. Number 0 or 1 after metric name indicates whether it was calculated for patients with or without obstructive sleep apnea.}\label{tab:second-test}
    \csvreader[
        tabular = | p{0.1925\textwidth} | p{0.1925\textwidth} | p{0.1925\textwidth} | p{0.1925\textwidth} |,
        table head = \hline \textbf{Metric} & \textbf{Centralized} & \textbf{Federated} & \textbf{Difference}\\\hline,
        late after line = \\\hline,
        separator = semicolon
    ]{media/second-test.csv}%
    {Metric=\metric, Centralized=\centralized, Federated=\federated, Difference=\difference}{%
        \metric & \centralized & \federated & \difference
    }
\end{table}

\subsubsection{Test framework / technique}

%Which test framework or technique was chosen and why? \label{q} \newline

No automated testing was written during the project. The model is manually tested by using evaluation and prediction scripts, which isolate some patients' measurements from the training procedure and later on execute predictions on them to give us representative results of model performance. The federated framework part of the project also does not have any special tests. Important to note is that the different hospitals, in different Docker containers do not share any patients' measurements data during training and testing, which is also the goal of federated learning.

%Which parts of the project were or were not tested, and why? \label{q} \newline

In production, besides automated testing of data pipeline, privacy that federated learning advertises should be thoroughly tested not to show any vulnerabilities of attacks described in Section~\ref{subsubsec:privacy-perserving-techniques}, such as inference attack.

\subsubsection{Security}

%Was security considered in the project and how was it addressed? \label{q} \newline

The whole concept of federated learning is build for the purpose of securing sensitive data by not sharing it to third parties, which is also what has been implemented in this proof-of-concept. In a multi-machine setup, Docker containers do not share any private patients' measurement data between each other. They merely exchange the knowledge in terms of model weights. Most additional security features mentioned in Section~\ref{subsubsec:privacy-perserving-techniques} were left out in favor of expanding the project towards the infrastructural direction by containerizing the implementation. While developing that, secure TLS communication was enforced in order for the gRPC communication between nodes to become encrypted and weights cannot be directly read by a middleman.

%Where do you see possible improvements in the project’s security? \label{q} \newline

Possible improvements in the project's security mostly entail differential privacy, which is already supported by Flower out-of-the box and offers a mostly straight-forward implementation. More difficult security features to further research and develop would be secure multiparty computation and homomorphic encryption. In case of progressing the project to Kuberenetes, it is important to understand how it can negatively affect the security that Flower brings and use an appropriate framework such as kubeFlower~\cite{parra-ullauriKubeFlowerPrivacypreservingFramework2024}.


\subsubsection{Improvements}

%Where do you see improvements in general? \label{q} \newline

Starting with a non-functional improvement: readability. The model code I took was a few months old and there is a more readable and clean model that a colleague at the company has developed since. Plugging in that model would be a highly beneficial next step. Afterward, running the federated network using docker on \emph{separate} networks would be one step closer to real implementation. Adding TLS certificates issued by an official authority like Let's Encrypt, instead of using self-signed certificates like I have done now, is a mandatory move; Let's Encrypt also offers test certificates, which could be great while exploring this part of security. Finally, reducing bandwidth and model weight size sent over network even more might be an interesting topic of research.


\subsubsection{Added value of the project}
%TOD also add a broader added value, e.g. for healthcare, so they can help more patients, faster, better, etc...
%TOD in addition, you provided 2 target audiences, but don't provide the added value for them?

%What do you consider the greatest added value of the project? \label{q} \newline

This prototype brings great flexibility to developers as they can swiftly gain understanding of the clear structure that Flower provides, they can adapt the code for other purposes due to its modular nature --- for example by switching to a different model for a different scenario --- and all of that, along with containerization, makes it possible to easily scale the prototype to a business-ready solution.

The greatest added value is ultimately for the patients, or any kind of clients whose data is used for the system. Besides better and faster diagnosis, most importantly, federated learning brings privacy. Privacy enables trust and there is no business without trust. This is the key impact that this approach brings compared to standard machine learning.

Beside patients, doctors receive improved tools, project managers and lawyers have less regulation burden, and scientists, together with the whole research community, can explore new solutions with the help of additional data that federated learning brings. Data scarcity is a problem with machine learning, especially in healthcare. Imagine that European hospitals create a federated network around the sensitive data, giving researchers the possibility to switch and explore different machine learning models with sufficient and realistic data, and with respect to each person's records.


\subsubsection{Future opportunities and next steps}

%What are the next steps or future opportunities for the project? \label{q} \newline

This project could be potentially adapted to any other machine learning project, especially those with privacy concerns or many IoT devices, sensors, moving devices, and so on. It could be used in many optimization scenarios, such as improving car safety features by learning on a fleet of vehicles without directly sending the data over the network, enhancing traffic light systems to reduce traffic jams, just to name a few possibilities. Mastering the implementation of a federated system might bring a company such as Result d.o.o a wide range of real-world project opportunities.

%\subsubsection{Next steps}
%
%What are the next steps or future opportunities for the project? \label{q} \newline
%
%Implement on computers in separate network and then in real hospitals.
%Implement on Kubernetes, big amount of devices.
