\subsection{General reflection}
\input{sections/reflection/general-reflection/general-reflection}

\subsection{Personal reflection}

%If you were to do the project again, what would you approach differently? \label{q} \newline

The project was planned well and the development went mostly smoothly. There are two small bits I would change if I did it again: (1) The remote server for machine learning that I had available holds a powerful graphics card. Knowing the difference in training speeds, I did my best to make it work on the federated training process. After having spent around a day if not more and with the help of three other employees, Python and Tensorflow successfully recognized it. The training was blazing was! Until Out Of Memory errors started to appear and through investigation, it was clear that the heavy apnea prediction model, simulated on three clients/hospitals, demanded somewhat more than 24 GB of available virtual RAM, which the powerful graphics card offered. This kept happening despite using a minimalistic dataset. Perhaps adding another such card to the server would solve the problem and was possible, but it was not reasonable, timewise. Switching back to CPU-only training there were no further hardware issues. (2) There was some notion of possibly getting live measurements data from a medical ring and making on-the-fly predictions, although we all knew that it is out of scope and would require almost a miracle or a big underestimation of requirements' implementation time. Making live ingestion pipelines is a whole other scene, so I should have never even thought about it and clearly mark it with ``Will not have'' importance.

%What impact do you think the or developed tool has on people (ethics/inclusion)? \label{q} \newline

\paragraph{Impact on people} Thinking about the impact of the matter on the people, it will most likely not bring as much notice as artificial intelligence did, as it is just one part of it. Although the bare concept can be very easily explained to almost any person and one can make sense out of it on its own, while understanding the fact that their sensitive data will remain stationary and under all regulations \emph{as it used to}, without any artificial intelligence model directly looking and processing it. This would give people less fear of artificial intelligence stealing their data, knowing that it will remain under protection of their hospital as before.

It is also worth to remind ourselves about the prediction bias that artificial intelligence models often cause. Whatever the source reason of the bias is, I have not done research on how federated learning concept might solve it, expect for the fact that with it, we can explore vast amounts of unrevealed private data and perhaps minimize bias that way.

Another impact the tool might have on people is that by knowing companies can use it to learn on your private data, one can feel even more pressure and become unsure about what is really going on and when he agreed. For example, I doubt most users of Google's Gboard smartphone keyboard knew federated learning concept was behind its next word suggestion feature~\cite{hardFederatedLearningMobile2019}, and that the suggestion knowledge was retrieved from someone else's private typing that contained who knows what. It might be beneficial to think about it from another perspective: A doctor also has lots of practical experience and has agreed not to share any personal data about his patients with others, although he has the right to treat any patient with all of his knowledge; this is exactly what federated learning concept tries to achieve.

%What impact do you think the research or developed tool has on society (economy/policy/education)? \label{q} \newline

\paragraph{Impact on society} Federated learning also has impact on society. Looking at it from the view of economy, it brings profit, since it can make better models with bigger data input and less bandwidth cost. From a policy perspective, it is a more compliant approach with less regulation burden. When inspecting it from an educational standpoint, there should not be much of an impact, expect perhaps for special education tools built on machine learning, for example flashcard app Anki\footnote{https://apps.ankiweb.net/} that uses Free Spaced Repetition Scheduler machine learning algorithm to find memory patterns~\cite{DeckOptionsAnki, 2023_OptimizingSpacedRepetition}. Imagine Anki's spaced repetition scheduler built using federated learning approach!

%What impact do you think the research or developed tool has on the climate (energy/sustainability)? \label{q} \newline

\paragraph{Impact on climate} The federated learning project can also have impact on climate. With its low bandwidth, it improves its climate footprint and aids in creating more efficient processes for practically anywhere to enable energy reduction. For example, federatively learning car driver's patterns to optimize driving parameters in the car's computer, reduce risks of accidents and fuel consumption~\cite{luCrossVehicleFederatedLearning2025}. Another example would be weather predictions, where we receive millions of measurements from sensors and satellites. This data could be preprocessed on the device itself and propagated through a federated network.

%What will stay with you most about the project? \label{q} \newline

As a final thought of reflection, the interest to learn more about machine learning field, especially its optimization capabilities, has grown during the project and will stay with me later on. I have never worked much with machine learning system, and now I see how much there is to learn and to gain.

% TODO: Titles in capitals.


\subsection{Feedback}

%What did you think overall about the integrated bachelor project and the distribution with the traineeship? \label{q} \newline

The integrated bachelor project was a wonderful experience and a perfect way to establish a strong connection with the industry and such good companies as Result d.o.o.\ I am especially glad my company mentor has kept in mind my profile --- my experience is more in software development and infrastructure rather than in artificial intelligence --- and arrange the traineeship to also have some machine learning, specifically hyperparameter tuning, in order for me to have some background and context before starting the bachelor project.

%Do you have suggestions for improvement for the integrated bachelor project? \label{q} \newline

From the university side, it was also very well organized. The intermediate assignments were not mandatory, which was a great move to keep you specially aware of the timeline, but not completely stressed about the deadlines. There are further possible improvements I can extract from the whole process of this bachelor thesis: (1) Introduce students to the powerful citation tools like Zotero. It is not completely obvious, but surely mandatory, and was not done in other courses before --- which could be possible, for example in IT \& Innovation where the reports and citations were already a big deal. (2) The research part of this document took most of the time, which meant less for implementation. If I am correct, there are research and development bachelor project types. In case that's right, perhaps also splitting the templates for each specific type would be worth a thought. (3) The person responsible for integrated bachelor project, in my case David Vandenbroeck, also my mentor, has warned me before going abroad that the individual integrated bachelor projects normally take more time and effort. Keep warning students about that, as it is very important, also in the planning phase to know that the scope could seem almost poor to be truly realistic.