\subsection{General Reflection}

\subsubsection{Achieved objectives}

Were the project objectives achieved? \label{q} \newline


\subsubsection{Test framework / technique}

Which test framework or technique was chosen and why? \label{q} \newline

Which parts of the project were or were not tested, and why? \label{q} \newline


\subsubsection{Security}

Was security considered in the project and how was it addressed? \label{q} \newline

Where do you see possible improvements in the project’s security? \label{q} \newline


\subsubsection{Improvements}

Where do you see improvements in general? \label{q} \newline


\subsubsection{Added value of the project}

What do you consider the greatest added value of the project? \label{q} \newline


\subsubsection{Future opportunities}

What are the next steps or future opportunities for the project? \label{q} \newline


\subsubsection{Next steps}

What are the next steps or future opportunities for the project? \label{q} \newline


\subsection{Personal Reflection}

If you were to do the project again, what would you approach differently? \label{q} \newline

What impact do you think the research or developed tool has on people (ethics/inclusion)? \label{q} \newline

What impact do you think the research or developed tool has on society (economy/policy/education)? \label{q} \newline

What impact do you think the research or developed tool has on the climate (energy/sustainability)? \label{q} \newline

What will stay with you most about the project? \label{q} \newline

% TODO: Titles in capitals.


\subsection{Feedback}

What did you think overall about the integrated bachelor project and the distribution with the traineeship? \label{q} \newline

Do you have suggestions for improvement for the integrated bachelor project? \label{q} \newline