\subsection{Background}

% What is the background of the company for which you carried out this project? Not applicable if the project was not conducted for a company. \label{q} \newline
The project was carried out at Result d.o.o.\ It is a software development company, but also with a focus on data, artificial intelligence, and business solutions. Result works on many projects, some of which are European. One such is eEarly --- an open platform for analysis and gathering of health data~\cite{EEarly}. It also provided the context for this bachelor thesis.

% Why would the company want this to be researched or developed? If not for a company: what is the motivation behind the bachelor project? \label{q} \newline
The European Union has many regulations and laws related to data, and there are even more for each individual country, organisation, and so on. This introduces challenges for projects like eEarly that utilize artificial intelligence and deal with sensitive medical data. The motivation for my bachelor thesis was to find the bridge between sensitive data, artificial intelligence, and a complex regulatory landscape.

% Manja's suggestion: V uvodu (poglavje 1.1. Background) še omeni, da bo bolj jasno, da je projekt usmerjen v uporabo biometričnih podatkov s senzorji in da bi se konkretno delalo na zaznavanju oz podpori diagnostiki za sleep anea-o. Da se uporabijo signali od oxygen saturationa, heart rate-a. Ker so občutljivi podatki in obiajno ostanejo na infrstrukturah od bolnišnic, je lahko to dejanski edge node uporabljen za federated learning.
The aim of this work was early diagnosis of sleep-related breathing disorders by analysing biometrical data. The main sources of data were APNEA HRV+SPO2 DATASET~\cite{julia-serdaAPNEAHRV+SPO2DATASET2023} and a smart medical ring Wellue O2Ring\footnote{https://getwellue.com/pages/o2ring-oxygen-monitor} that a person can wear while it continuously performs medical measurements. The artificial intelligence model used heart rate and oxygen saturation (SpO2) to retrospectively label patients' measurements and indicate periods consistent with a sleep-related breathing disorder called obstructive sleep apnea (OSA)~\cite{strolloObstructiveSleepApnea1996}.


\subsection{Problem statement}

% What is the problem statement? \label{q} \newline
In an ideal situation, an artificial intelligence model could train on all data without restrictions. In reality, besides strict European Union laws, such as General Data Protection Regulation (GDPR)~\cite{sasirekhaSystematicReviewPrivacypreserving2025, prayitnoSystematicReviewFederated2021}, each hospital normally keeps its data isolated. This reveals the main issue: An artificial intelligence model can --- without considerable legal and data privacy effort --- only train on one hospital. Consequences of this are poor model performance with less accurate predictions, and the new technologies are not being utilized fully~\cite{abdallaFutureArtificialIntelligence2025}. From this follows the proposal, which is not to loosen the law, but to explore techniques like federated learning~\cite{FederatedLearning2026} to satisfy both the regulations and the artificial intelligence's demand for data.


\subsection{Intention}

% What is the company’s intention? If not for a company: how will the product be used in the long term (independently of a company)? \label{q} \newline
The main intention of the project is to develop a federated learning proof-of-concept (POC) for the company, which can later be used as a starting point for other projects and might be fully implemented, possibly in a healthcare environment. It might also become a new privacy-oriented artificial intelligence solution that the company could offer to clients for commercialization as a reusable asset.


\subsection{Scope within the bachelor thesis (MVP – need to have)}

% What is the scope of the project within this bachelor project? \label{q} \newline

%TOD I would add also in short, what your proof of concept at least should be able to do after the bachelor project

The minimal scope includes a simulation of federated learning on a single machine only with Python and without any containerization such as Docker. The scope can be seen on the Table~\ref{tab:requirements-with-scope} on page~\pageref{tab:requirements-with-scope} with additional details in Appendix~\ref{appendix:backlog}. The requirement descriptions include terminology introduced in Section~\ref{sec:preliminary-research}. ``Must have'' features describe the minimal viable product (MVP); without these, the project is not deemed finished, unless blockers are clearly stated.

\subsection{Ultimate scope (want to have)}

%What is the ultimate scope? \label{q} \newline

%TOD likewise, also add in short what the dream product would be
The prototype in its most complete form would be a simulation of federated learning on four machines --- one global model and three hospitals --- using a containerization technology like Docker, and the machines would communicate from separate networks with security features such as TLS and differential privacy. Ultimate scope of the project is further defined with features of ``Should have'' and ``Could have'' importance in the Table~\ref{tab:requirements-with-scope} on page~\pageref{tab:requirements-with-scope}. As importance lowers, features become closer to those of realistic setting in which federated learning could be deployed, and more unknown challenges might appear.